---
title: "Barbeque Restaurant Map"
author: "Kenneth W. Moffett"
date: "June 3, 2017"
output: html_document
---

This is a map of some of the Barbeque restaurants that I like that are located in the United States.

# Load Leaflet Package and Dataset

This data frame contains the following information: Barbeque restaurant name, the longitude and latitude locations of the restaurants, adn the address/location of each of the restaurants. 

```{r}
library(leaflet)
data <- read.csv("Barbeque Restaurants.csv", header = TRUE)
```

# View the Data

```{r}
data
```

# Make Markers in the Graph Provide Address and Location


```{r}
restaurantpopup <- paste0("<strong>", data$restaurant, "</strong>", "<br>", "Address: ", data$address, "<br>", "City, State and Zip: ", data$location)
```

# Barbeque Restaurants Map

This map shows the locations, along with a popup for each that tells you the restaurant name, the address, city, state, and the zip code in which it is located.

```{r, echo = FALSE}
my_map2 <- data %>% 
  leaflet() %>%
  addTiles() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  addMarkers(~longitude, ~latitude, popup = ~ restaurantpopup, label = ~ restaurant)
my_map2
```